Medical Concept Extraction

### 2012-12-17 paper/paper.tex
asses

Namely, we used the Porter Stemming Algorithm, as developed by Martin Porter.  This particular stemming algorithm is divided into a number of linear steps. Word letters are first replaced by symbols for vowels, $V$, and consonants, $C$. The measure, $m$, of the word is computed as the number of repetitions of the pattern $VC$, and this is used to determine whether suffixes ought to be removed. Plural word forms are then removed such as  sses $\rightarrow$ ss and removal of trailing s's; followed by the removal of past participles; and finally terminal y's are replaced with i's. Subsequent steps handle different orderings of suffixes by translating double suffixes into a single suffix and then removing suffixes under certain predefined conditions.

>>>>

Namely, we used the Porter Stemming Algorithm, as developed by Martin Porter.  This particular stemming algorithm is divided into a number of linear steps. Word letters are first replaced by symbols for vowels, $V$, and consonants, $C$. The measure, $m$, of the word is computed as the number of repetitions of the pattern $VC$, and this is used to determine whether suffixes ought to be removed. Plural word forms are then removed such as  $sses \rightarrow ss$ and removal of trailing s's; followed by the removal of past participles; and finally terminal y's are replaced with i's. Subsequent steps handle different orderings of suffixes by translating double suffixes into a single suffix and then removing suffixes under certain predefined conditions.
